---
title: "Lab6 Vignette"
author: "Niclas Lovsjö and Maxime Bonneau"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r,include=FALSE}
library(Lab6)
library(parallel)
```
This lab is about writing fast code. We have included 3 types of algorithms for solving the knapsack optimization problem. We have a brute force, a dynamic programming and a greedy approach. We will use this vignette to comment about our results. 
  
_**Brute force search**_  
  
**Question:** *How long time does it take to run the brute force algorithm with n=16?*
  
```{r}
set.seed(42)
n <- 16
knapsack_objects <-
        data.frame(
                w=sample(1:4000, size = n, replace = TRUE),
                v=runif(n = n, 0, 10000)
        )
system.time(brute_force_knapsack(knapsack_objects,2000))
```


_**Dynamic programming**_  
  
**Question:** *How long time does it take to run the algorithm for n=500 objects?*
```{r}
set.seed(42)
n <- 500
knapsack_objects <-
        data.frame(
                w=sample(1:4000, size = n, replace = TRUE),
                v=runif(n = n, 0, 10000)
        )
system.time(knapsack_dynamic(knapsack_objects,2000))
```
  
  
_**Greedy heuristic**_

**Question:** *How long time does it take to run the algorithm for n=1000000 objects?*

```{r}
n <- 1000000
knapsack_objects <-
        data.frame(
                w=sample(1:4000, size = n, replace = TRUE),
                v=runif(n = n, 0, 10000)
        )
  
system.time(greedy_knapsack(knapsack_objects,W=2000))
```

_**Profiling**_

**Question:** *How large performance gain could you get by trying to improving your code?*

We didnt find any particular bottlenecks using lineprof.
  
_**Parallelize brute force**_

**Question:** *How large performance gain could you get by parallelizing brute force search?*
  
Since we had to re-do our brute-force, we will compare the parallelized one with the re-made one not using the mclapply-function.
```{r}
n <- 16
knapsack_objects <-
        data.frame(
                w=sample(1:4000, size = n, replace = TRUE),
                v=runif(n = n, 0, 10000)
        )
system.time(brute_force_knapsack_para_nopara(knapsack_objects,W=2000))
system.time(brute_force_knapsack_para(knapsack_objects,W=2000))
```

